Predicting the (non-cryptographic) PCG Pseudo-Random Number Generator In Practice

### 2020-06-01 article/main.tex
micro stuff

\subsection{Application to the \texttt{Lehmer64} generator}

Adapting the previous reasoning enables an efficient state reconstruction
algorithm for the \texttt{Lehmer64} generator shown in
Fig.~\ref{fig:prngs}. When clocked, it outputs the top 64 bits of a geometric
sequence ($k=128$ and $\ell=64$). Three successive outputs are sufficient to
reconstruct the internal state using Babai's rounding technique. This yields the
following reconstruction algorithm:
\begin{minted}[fontsize=\scriptsize]{python}
def reconstruct(X):
    """
    Produce the internal state of the generator given three consecutive outputs.
    16 multiplications, 1 division, 11 additions and 3 roundings only.
    """
    a = 0xda942042e4dd58b5
    r = round(2.64929081169728e-7 * X[0] + 3.51729342107376e-7 * X[1] + 3.89110109147656e-8 * X[2])
    s = round(3.12752538137199e-7 * X[0] - 1.00664345453760e-7 * X[1] - 2.16685184476959e-7 * X[2])
    t = round(3.54263598631140e-8 * X[0] - 2.05535734808162e-7 * X[1] + 2.73269247090513e-7 * X[2])
    u = r * 1556524 + s * 2249380 + t * 1561981
    v = r * 8429177212358078682 + s * 4111469003616164778 + t * 3562247178301810180
    state = (a*u + v) % (2**128)
    return state
\end{minted}

But enough fooling around. Let's go back to \textsf{PCG64}.

>>>>

\subsection{Application to the \texttt{lehmer64} generator}

Adapting the previous reasoning enables an efficient state reconstruction
algorithm for the \texttt{lehmer64()} generator shown in
Fig.~\ref{fig:prngs}. When clocked, it outputs the top 64 bits of a geometric
sequence ($k=128$ and $\ell=64$). Three successive outputs are sufficient to
reconstruct the internal state using Babai's rounding technique. This yields the
following reconstruction algorithm:
\begin{minted}[fontsize=\scriptsize]{python}
def reconstruct(X):
    """
    Produce the internal state of the generator given three consecutive outputs of lehmer64().
    16 multiplications, 1 division, 11 additions and 3 roundings only.
    """
    a = 0xda942042e4dd58b5
    r = round(2.64929081169728e-7 * X[0] + 3.51729342107376e-7 * X[1] + 3.89110109147656e-8 * X[2])
    s = round(3.12752538137199e-7 * X[0] - 1.00664345453760e-7 * X[1] - 2.16685184476959e-7 * X[2])
    t = round(3.54263598631140e-8 * X[0] - 2.05535734808162e-7 * X[1] + 2.73269247090513e-7 * X[2])
    u = r * 1556524 + s * 2249380 + t * 1561981
    v = r * 8429177212358078682 + s * 4111469003616164778 + t * 3562247178301810180
    state = (a*u + v) % (2**128)
    return state
\end{minted}

But enough fooling around; let's go back to \textsf{PCG64}.
